Out-of-Sample Comparisons of Overfit Models

### 2016-12-22 paper.tex
[#52] Tweak date/version script to use bashful w/in the LaTeX paper
Closes #52

Statistics like $\oost$ have a long history in empirical economics
because they capture an intuitive idea of model fit: that a good model
should be able to forecast well on new data. \cite{MeR:83}
use such a statistic to study exchange rate models and find that none
of the models that existed at the time of their study outperform a
random walk. This finding has been remarkably durable and has spawned
an enormous literature; see \cite{Mar:95}, \cite{KiT:03},
\cite{CCP:05}, \cite{EnW:05}, \cite{Ros:05}, and \cite{BWB:10}, among
many others. Research in financial markets has found a similar pattern,
e.g. \cite{BoH:99}, \citet{GoW:08,GoW:03}, and \citet{Tim:08}.

@@

\tryinput{floats/mc-ftest.tex}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% End:

>>>>

@@

\clearpage
\markboth{}{}
\tryinput{floats/mc-ftest.tex}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% TeX-command-extra-options: "-shell-escape"
%%% End:
